RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-29 assets/illustration/energy_distribution.tex
:bento: Update assets

\begin{tikzpicture}
	\begin{axis}[
			clip mode=individual,
			height=5cm,
			width=9cm,
			xlabel = $z$,
			ylabel = {Probability Density},
			font=\scriptsize,
			no markers,
			xmin=0,
			ymin=0,
			xmax=70,
			xtick={0,12.78,20.28,29.62,70},
			xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},
			yticklabels=\empty,
			samples = 200
		]

>>>>

\begin{tikzpicture}
	\begin{axis}[
			clip mode=individual,
			height=4cm,
			width=10cm,
			xlabel = $z$,
			ylabel = {Probability Density},
			font=\normalsize,
			no markers,
			xmin=0,
			ymin=0,
			xmax=70,
			xtick={0,12.78,20.28,29.62,70},
			xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},
			yticklabels=\empty,
			samples = 200
		]

### 2022-10-29 assets/illustration/input_distribution.tex
:truck: Rename files
:bento: Update assets
:bento: Update illustrations

\begin{tikzpicture}
	\begin{groupplot}
		[group style={
					rows=3,
					group name=plots,
					x descriptions at=edge bottom,
					y descriptions at=edge left,
					vertical sep=10
				},
			ybar,
			xmin=0,
			xmax=4,
			xtick={1,2,3,4},
			ymin=0,
			ymax=1,
			xlabel={Reflection State},
			enlarge x limits={value=0.25,upper},
			enlarge y limits={value=0.1,upper},
			width=10cm,
			height=3cm,
			every axis plot/.append style={bar shift=0}
		]
		\nextgroupplot
		\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
		\legend{SR}
		\nextgroupplot[ylabel={Probability Distribution}]
		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
		\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
		\legend{IRS}
		\nextgroupplot
		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.125)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.625)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
		\legend{Metascatter}
	\end{groupplot}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
	\begin{groupplot}
		[group style={
					rows=3,
					group name=plots,
					x descriptions at=edge bottom,
					y descriptions at=edge left,
					vertical sep=10
				},
			ybar,
			xmin=0,
			xmax=4,
			xtick={1,2,3,4},
			ymin=0,
			ymax=1,
			xlabel={Reflection State},
			enlarge x limits={value=0.25,upper},
			enlarge y limits={value=0.1,upper},
			width=10cm,
			height=2.6cm,
			every axis plot/.append style={bar shift=0}
		]
		\nextgroupplot
		\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0.25)};
		\legend{BackCom/AmBC/SR}
		\nextgroupplot[ylabel={Probability Distribution}]
		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,1)};
		\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
		\legend{RIS}
		\nextgroupplot
		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(1,0.125)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(2,0.625)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(4,0)};
		\legend{RIScatter}
	\end{groupplot}
\end{tikzpicture}

### 2022-10-29 assets/illustration/time_structure.tex
:bento: Update assets

\begin{tikzpicture}
	% BC/AmBC/SR
	\foreach \x in {0,...,3}{
			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {4,...,7}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,11}{
			\draw[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {12,...,15}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}

@@

	\foreach \x in {1,...,7}{
			\draw[dotted] (\x,1) -- (\x,3.75);
		}
	\draw[latex-latex] (0,3.5) -- (0.5,3.5) node[above,midway,yshift=1]{PB};
	\draw[latex-latex] (0,4.1) -- (1,4.1) node[above,midway,yshift=1]{BB};
	\draw[latex-latex] (0,4.7) -- (8,4.7) node[above,midway,yshift=1]{Channel Block};

>>>>

\begin{tikzpicture}[font=\large]
	% BC/AmBC/SR
	\foreach \x in {0,...,3}{
			\draw[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {4,...,7}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,11}{
			\draw[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {12,...,15}{
			\draw[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}

@@

	\foreach \x in {1,...,7}{
			% \draw[dotted] (\x,1) -- (\x,3.75);
			\draw[dotted] (\x,1) -- (\x,3.25);
		}
	\draw[latex-latex] (0,1.4) -- (0.5,1.4) node[above,midway,yshift=1]{PB};
	% \draw[latex-latex] (0,4.1) -- (1,4.1) node[above,midway,yshift=1]{BB};
	\draw[latex-latex] (0,2.4) -- (1,2.4) node[above,midway,yshift=1]{BB};
	\draw[latex-latex] (0,3.4) -- (8,3.4) node[above,midway,yshift=1]{Channel Block};

### 2022-10-29 assets/simulation/region_comparison.tex
:bento: Update assets

\begin{axis}[%
width=4.079in,
height=3.432in,
at={(0.684in,0.463in)},
scale only axis,
xmin=0,
xmax=7.08488905081188,
xlabel style={font=\color{white!15!black}},
xlabel={Primary Rate [bits/s/Hz]},
ymin=0,
ymax=2,
ylabel style={font=\color{white!15!black}},
ylabel={Total Backscatter Rate [bits/BSP]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.03)}, anchor=south west, legend cell align=left, align=left, draw=white!15!black},
title style={font=\LARGE},
label style={font=\LARGE},
ticklabel style={font=\Large},
legend style={font=\Large},
reverse legend,
every axis plot/.append style={line width=2pt}
]
\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
6.41670947751651	1.6054968458145\\
0	1.6054968458145\\
0	0\\
7.08488904258997	0\\
7.08488904258997	4.1836174712136e-07\\
6.90245078291004	1.01381402853452\\
6.6407882228124	1.4980015567956\\
6.57239022993099	1.55479524496005\\
6.51932412280019	1.58378871636645\\
6.49722825073873	1.59220191008592\\
6.4775306470264	1.59794430837116\\
6.4598927531162	1.60170353740201\\
6.44402970380102	1.60398330481762\\
6.43668727400095	1.6046886802456\\
6.42970223763566	1.60515550025508\\
6.42700280669212	1.60528273332009\\
6.42435520073694	1.60537879376922\\
6.4217579842616	1.60544542043883\\
6.41920966721981	1.60548425498564\\
6.41670947751651	1.6054968458145\\
};
\addlegendentry{RIScatter}

>>>>

	\begin{axis}[%
			width=4.079in,
			height=1.587in,
			at={(0.684in,0.361in)},
			scale only axis,
			xmin=0,
			xmax=7.08488905081188,
			xlabel style={font=\color{white!15!black}},
			xlabel={Primary Rate [bits/s/Hz]},
			ymin=0,
			ymax=2,
			ylabel style={font=\color{white!15!black}},
			ylabel={Total Backscatter\\Rate [bits/BB]},
			axis background/.style={fill=white},
			xmajorgrids,
			ymajorgrids,
			legend style={at={(0.03,0.03)}, anchor=south west, legend cell align=left, align=left, draw=white!15!black},
			title style={font=\LARGE},
			label style={font=\LARGE},
			ticklabel style={font=\Large},
			legend style={font=\Large},
			reverse legend,
			every axis plot/.append style={line width=2pt},
			align=center
		]
		\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, mycolor1}]
		table[row sep=crcr]{%
				6.41670947751651	1.6054968458145\\
				0	1.6054968458145\\
				0	0\\
				7.08488904258997	0\\
				7.08488904258997	4.1836174712136e-07\\
				6.90245078291004	1.01381402853452\\
				6.6407882228124	1.4980015567956\\
				6.57239022993099	1.55479524496005\\
				6.51932412280019	1.58378871636645\\
				6.49722825073873	1.59220191008592\\
				6.4775306470264	1.59794430837116\\
				6.4598927531162	1.60170353740201\\
				6.44402970380102	1.60398330481762\\
				6.43668727400095	1.6046886802456\\
				6.42970223763566	1.60515550025508\\
				6.42700280669212	1.60528273332009\\
				6.42435520073694	1.60537879376922\\
				6.4217579842616	1.60544542043883\\
				6.41920966721981	1.60548425498564\\
				6.41670947751651	1.6054968458145\\
			};
		\addlegendentry{RIScatter}
